Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-01 overview.tex
Added description of Dedner MHD solver to the overview section.

\subsubsection{Godunov MUSCL (HD) with Dender divergence cleaning (MHD)}

>>>>

\subsubsection{Godunov MUSCL (HD) with Dedner divergence cleaning (MHD)}
This solver was developed by Wang \& Abel to attack problems in
magnetic field amplification during the formation of galaxies
\citep{Wang:2009a} and to understand the role proto-stellar jets for
the theory of star formation \citep{Wang:2009b}. It combines the standard
approach of Godunov \citep{Godunov1959} for finite volume techniques
with the method of lines as described as e.g. by
\cite{leveque2002finite} and \cite{toro-1997}. In addition, however,
it implements the hyperbolic divergence cleaning algorithm of
\cite{2002JCoPh.175..645D}. It supports multiple approximate Riemann
solvers and supports non-ideal equations of states. Consequently,
these suite of solvers can be used for hydro and magneto-hydrodynamic
simulations. It is also this class of solvers as well as a version of
the PPM hydro solver which have been ported to Nvidia's CUDA framework
allowing enzo to take advantage of modern graphics hardware \citep{Wang:2010}.
